---
title: "Matrix Multiplication"
author: "Shubham Patil"
date: "07/08/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Matrix Multiplication Applet

* This is an attempt to simplify the multiplication of two standard 3 by 3 matrices often encountered in preliminary maths.
* This applet will be pretty useful for non programmers created with the help of shiny package in R.

## Example

Here's an example of the matrix multiplication.

```{r}
print("Given two 3 by 3 matrices as:")
A = matrix(rep(1, 9), 3, 3)
B = matrix(rep(1, 9), 3, 3)
print("A:")
print(A)
print("B:")
print(B)
```
## Result

```{r}
print("Resultant Matrix A * B:")
print(A %*% B)
```



## Instructions to use applet

* Note that the demo matrices are filled with 1's by default.
* You can change the inputs as you like.
* The result is displayed on the main panel under the heading 'A * B'.
* For more information about creating an applet like this, refer [shiny](shiny.rstudio.com)

## Thank You
